Handovers - SIPHER 7 Equivalent Income

### 2023-09-03 minos/outcomes/equivalent_income_out_batch.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=TRUE)
wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=TRUE)
```

@@

base.batch <- calc_age_group(base.batch)
wage.batch <- calc_age_group(wage.batch)
energy.batch <- calc_age_group(energy.batch)
```

@@

```{r}
equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
```

@@

all.combined <- rbind(base.subset, wage.subset, energy.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis'))

@@

```{r}
equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
```

@@

## Living Wage

@@

### Income and Equivalent Income

@@

income_equivinc_change_batch(base.batch, energy.batch)
income_equivinc_change_batch(base.batch, wage.batch)
```

### Percent Change

@@

income_equivinc_percent_change_batch(base.batch, energy.batch)
income_equivinc_percent_change_batch(base.batch, wage.batch)

#### By Subpopulation

@@

#### On the Same Plot

@@

# 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')

equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')

equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
```

```{r}
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')
```

## Energy Crisis

```{r}
S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
  base.hous <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')

@@

### Housing Quality

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
```

### Neighbourhood Safety

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
```

### Mental Wellbeing

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
```

### Physical Health

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
```

### Loneliness

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
```

### Labour State

```{r}
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
```

>>>>

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
```

@@

base.batch <- calc_age_group(base.batch)
wage.batch <- calc_age_group(wage.batch)
energy.batch <- calc_age_group(energy.batch)
child.batch <- calc_age_group(child.batch)
pov.batch <- calc_age_group(pov.batch)
```

@@

```{r}
equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'AllChild')
equivalent_income_comparison_fullpop_batch(base.batch, pov.batch, 'PovertyChild')
```

@@

child.subset <- child.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'AllChild')

pov.subset <- pov.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'PovertyChild')

all.combined <- rbind(base.subset, wage.subset, energy.subset, child.subset, pov.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis', 'AllChild', 'PovertyChild'))

@@

```{r}
equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
equivalent_income_comparison_treated_batch(base.batch, child.batch, 'AllChild')
equivalent_income_comparison_treated_batch(base.batch, pov.batch, 'PovertyChild')
```

@@

@@

## Income and Equivalent Income

@@

income_equivinc_change_batch(base.batch, energy.batch)
income_equivinc_change_batch(base.batch, wage.batch)
income_equivinc_change_batch(base.batch, child.batch)
income_equivinc_change_batch(base.batch, pov.batch)
```

## Percent Change

@@

income_equivinc_percent_change_batch(base.batch, energy.batch)
income_equivinc_percent_change_batch(base.batch, wage.batch)
income_equivinc_percent_change_batch(base.batch, child.batch)
income_equivinc_percent_change_batch(base.batch, pov.batch)
```

### By Subpopulation

@@

### All Subgroups

@@

S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
  base.hous <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')

@@

#### Energy Crisis

```{r}
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
```

#### Living Wage

```{r}
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_labour_state')
```

#### All Child

```{r}
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_labour_state')
```

#### Poverty Child

```{r}
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_labour_state')
```

### 2023-09-03 minos/validation/cross_validation_S7.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

```{r}

```

>>>>

# Parity

```{r}
cv.parity <- cv %>%
  filter(sex == "Female")

raw.parity <- raw %>%
  filter(sex == "Female")

parity.pivoted <- combine_and_pivot_long(df1 = cv.parity, 
                                          df1.name = 'simulated', 
                                          df2 = raw.parity, 
                                          df2.name = 'raw', 
                                          var = 'nkids_ind')

cv_ordinal_plots(pivoted.df = parity.pivoted, 
                 var = 'nkids_ind',
                 save = FALSE)
rm(educ.pivoted)
```

# Job NSSEC

```{r}
job_sec.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'job_sec')

cv_ordinal_plots(pivoted.df = job_sec.pivoted, 
                 var = 'job_sec',
                 save = FALSE)
rm(mstat.pivoted)
```

### 2023-09-03 minos/validation/handovers.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

>>>>

## Job Sec

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'job_sec')

tit <- 'Job NSSEC'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = job_sec, colour = job_sec)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=job_sec)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'job_sec.png',
         plot = last_plot(),
         path = save.path)
}

### 2023-09-03 minos/validation/handovers_S7.Rmd
Testing the addition of a job_sec module for transitioning to different job types. Could be quite important for equivalent income

```{r}

```

>>>>

## Job Sec

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'job_sec')

tit <- 'Job NSSEC'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = job_sec, colour = job_sec)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=job_sec)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'job_sec.png',
         plot = last_plot(),
         path = save.path)
}

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat,
                                  df1.name = 'simulated', 
                                  df2 = raw.dat, 
                                  df2.name = 'raw', 
                                  var = 'job_sec')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'job_sec',
                 save = shall.we.save,
                 save.path = save.path)
```
